\chapter*{Conclusion}
\addcontentsline{toc}{chapter}{Conclusion}

Congratulations on completing this study guide for the \textbf{IBM Watsonx Generative AI Engineer Associate (C1000-185)} certification.

If you have worked through every chapter, every practice question, and the mock exam in Appendix~\ref{app:mock}, you are ready to sit the exam.

\section*{What you have learned}

\begin{itemize}[leftmargin=*]
    \item \textbf{Chapter~\ref{ch:foundations}} — the five capabilities, GenAI patterns (Transformer, MoE, VAE, reasoning), watsonx model catalogue, billing classes, Granite Guardian.
    \item \textbf{Chapter~\ref{ch:prompting}} — zero/few-shot, chain-of-thought, decoding methods, parameter control, prompt templates, prompt risks.
    \item \textbf{Chapter~\ref{ch:fine-tuning}} — the biggest section: hard vs soft prompts, LoRA / QLoRA, quantisation, InstructLab + LAB method, synthetic-data generator (Kolmogorov–Smirnov, Anderson–Darling, differential privacy).
    \item \textbf{Chapter~\ref{ch:rag}} — embeddings, vector stores, retrievers, LangChain + LlamaIndex patterns, agentic RAG, AutoRAG.
    \item \textbf{Chapter~\ref{ch:deployment}} — Deployment Spaces, online vs batch, Model Gateway, governance, SaaS vs Cloud Pak.
    \item \textbf{Chapter~\ref{ch:integration}} — SDK + REST integration, LangChain agents, Model Context Protocol, real-world architectures.
\end{itemize}

\section*{Next steps}

\begin{enumerate}[leftmargin=*]
    \item \textbf{Take the mock exam} — Appendix~\ref{app:mock}. Score yourself with Appendix~\ref{app:answers}.
    \item \textbf{Hands-on practice} — run every script in \texttt{labs/lab-01} through \texttt{labs/lab-06} in your own watsonx.ai project.
    \item \textbf{Review weak areas} — spend more time on Chapter~\ref{ch:fine-tuning}; it is 31\% of the exam.
    \item \textbf{Schedule the exam} when you score 75\%+ on the mock under timed conditions.
    \item \textbf{Stay current} — the watsonx model catalogue changes every quarter; follow IBM watsonx release notes and \href{https://ruslanmv.com}{ruslanmv.com} for updates to this book.
\end{enumerate}

\section*{Exam-day tips}

\begin{itemize}[leftmargin=*]
    \item Read carefully — watch for \emph{MOST}, \emph{BEST}, \emph{LEAST}, \emph{NOT}.
    \item Eliminate two obviously-wrong options before reasoning between the last two.
    \item Flag and move — never burn five minutes on one question.
    \item Budget: $\sim$87 s per question. Set mental checkpoints at 30, 60, and 75 minutes.
    \item Trust your preparation. First instinct beats second-guessing.
    \item Never leave a question blank — there is no penalty for wrong answers.
\end{itemize}

\section*{After you certify}

\begin{itemize}[leftmargin=*]
    \item Add the badge to LinkedIn and your résumé — IBM issues a Credly badge automatically.
    \item Share what worked. A short blog post or LinkedIn write-up helps the next batch of candidates.
    \item Build something real on watsonx.ai — the labs in this repository are a starting point, not the destination.
    \item Look at the next tier: the \emph{IBM watsonx AI Engineer (Professional)} certification covers production governance, multi-agent systems, and enterprise integration in depth.
    \item Continue the series: \href{https://github.com/ruslanmv/agentic-ai-tutorial}{Agentic AI from Scratch} and the \href{https://github.com/ruslanmv/watsonx-workshop}{watsonx Workshop}.
\end{itemize}

\cleardoublepage

% ----------------------------------------------------------------------------
% About the Author
% ----------------------------------------------------------------------------

\chapter*{About the Author}
\addcontentsline{toc}{chapter}{About the Author}

\noindent\textbf{Ruslan Idelfonso Magana Vsevolodovna} is a senior AI engineer and IBM watsonx practitioner. He has spent more than a decade building production AI for enterprises in finance, telecoms, and the public sector, and now teaches what he learns on YouTube, Udemy, and his blog at \href{https://ruslanmv.com}{ruslanmv.com}.

\medskip

His tutorial series includes:

\begin{itemize}[leftmargin=*]
    \item \textbf{Agentic AI from Scratch} — building production agents in LangChain, LangGraph, and CrewAI. \\
          \href{https://github.com/ruslanmv/agentic-ai-tutorial}{github.com/ruslanmv/agentic-ai-tutorial}
    \item \textbf{watsonx Workshop} — end-to-end RAG application on watsonx with accelerator notebooks. \\
          \href{https://github.com/ruslanmv/watsonx-workshop}{github.com/ruslanmv/watsonx-workshop}
    \item \textbf{watsonx Generative AI Engineer Cert Prep} — this book and its companion YouTube and Udemy editions. \\
          \href{https://github.com/ruslanmv/IBM-Watsonx-Generative-AI-Engineer-Certification}{github.com/ruslanmv/IBM-Watsonx-Generative-AI-Engineer-Certification}
\end{itemize}

\medskip

\noindent\textit{“Build it on the platform, prove it with metrics, then explain it like a teacher.”}

\medskip

\noindent\textbf{Connect:}
\href{https://ruslanmv.com}{ruslanmv.com} \textbullet\
\href{https://www.linkedin.com/in/ruslanmv/}{LinkedIn} \textbullet\
\href{https://github.com/ruslanmv}{GitHub}

\vspace{1cm}

\noindent\textit{If this book helped you pass, star the GitHub repository and tell a colleague. Word of mouth is how this series grows.}

\cleardoublepage

% ----------------------------------------------------------------------------
% Also by the Same Author
% ----------------------------------------------------------------------------

\chapter*{Also by the Same Author}
\addcontentsline{toc}{chapter}{Also by the Same Author}

\begin{itemize}[leftmargin=*]
    \item \textbf{Agentic AI from Scratch — LangChain, LangGraph, CrewAI} (open-source course \& slide decks)
    \item \textbf{watsonx Workshop — End-to-End RAG on IBM watsonx} (open-source course)
    \item Articles and tutorials at \href{https://ruslanmv.com}{ruslanmv.com}
\end{itemize}

\vspace{1cm}

\noindent\rule{\linewidth}{0.4pt}

\medskip

\small\noindent
IBM, watsonx, watsonx.ai, watsonx.data, watsonx.governance, Granite, Slate, and InstructLab are trademarks or registered trademarks of IBM Corporation. This study guide is an independent, community publication and is not authorised, sponsored, or otherwise approved by IBM Corporation.

\cleardoublepage
