\chapter{Glossary}
\label{app:glossary}

A quick-reference dictionary of the terms used in this book and on the C1000-185 exam. Where a term has a current 2026 watsonx model ID associated with it, the ID is listed.

\begin{description}[leftmargin=*,style=nextline]
\item[Adapter] A small, trainable add-on to a frozen base model. LoRA is the most common example.
\item[Agent] An LLM-driven controller that picks tools, executes them, and loops until a goal is met. See ReAct.
\item[Agentic RAG] RAG where the agent decides when and how to retrieve, possibly multiple times.
\item[AI Pipelines] watsonx's managed scheduler for data and AI jobs (ingest, embed, index, evaluate).
\item[Anderson--Darling test] Statistical test for distribution similarity, weighted toward the tails. Used to validate synthetic data quality.
\item[AutoRAG] Automatic hyperparameter search over the RAG pipeline (chunk size, embedder, $k$, re-ranker).
\item[Base model] An untuned next-token predictor (e.g.\ \texttt{ibm/granite-3-8b-base}). Starting point for fine-tuning.
\item[BF16 / FP16 / FP32] Floating-point precisions used in model weights. Smaller = cheaper memory and bandwidth.
\item[Billing class] watsonx pricing tier (Class 1/2/3/12/13). Higher class = stronger model = higher cost per million tokens.
\item[Chain] LangChain primitive: a linear or DAG sequence of prompts and parsers.
\item[Chain-of-Thought (CoT)] Prompting technique: ``think step by step'' before answering.
\item[Chat model] An instruct model further tuned for multi-turn conversation with system / user / assistant roles.
\item[Chunking] Splitting documents into pieces for embedding and retrieval.
\item[Cloud Pak for Data] IBM's on-prem / multi-cloud distribution of watsonx (Software model).
\item[Context window] The maximum number of tokens (input + output) a model can process at once.
\item[CRISPE / APE / CARE] Prompt-design frameworks. CRISPE = Capacity, Request, Insight, Style, Personality, Experiment.
\item[Data Refinery] Visual data-prep tool in watsonx.ai for profiling and cleaning datasets.
\item[Decoding] How the next token is chosen: \texttt{greedy} (argmax) or \texttt{sample} (with temperature / top-k / top-p).
\item[Deployment Space] Permission-scoped, audited container for promoted assets and REST endpoints. Production sibling of a Project.
\item[Differential privacy] Algorithmic noise that makes the presence of any one record statistically undetectable in outputs. Controlled by privacy budget $\varepsilon$, leakage probability $\delta$, and random seed.
\item[Embedding] A dense vector of floats representing the meaning of a piece of text.
\item[Factsheet] A governance artefact summarising a model version: intended use, evaluation results, known limitations.
\item[Few-shot prompting] Including 2--5 worked input/output examples in the prompt.
\item[Foundation model] A large model trained on broad data, ready for many downstream tasks.
\item[Full fine-tuning] Updating every weight in the model. Highest cost, highest risk of forgetting, sometimes highest quality.
\item[Granite] IBM's foundation-model family. Default IBM-native answer on this exam. Current: \texttt{ibm/granite-3-2-8b-instruct}, \texttt{ibm/granite-3-3-8b-instruct}, \texttt{ibm/granite-code-3-8b-instruct}.
\item[Granite Embedding] IBM's multilingual embedding family: \texttt{ibm/granite-embedding-107m-multilingual}, \texttt{ibm/granite-embedding-278m-multilingual}.
\item[Granite Guardian] IBM's safety-filter classifier family: \texttt{ibm/granite-guardian-3-8b}, \texttt{ibm/granite-guardian-3-2-5b}. Detects harm, bias, jailbreaks, ungrounded answers.
\item[Greedy decoding] Always pick the highest-probability next token. Deterministic.
\item[Hallucination] Confident, plausible-sounding output that is factually wrong.
\item[Hard prompt] Human-readable text tokens, written by a person.
\item[HAP] Hate, Abuse, Profanity --- a category of output filters.
\item[HNSW] Hierarchical Navigable Small World, the most popular vector-index algorithm in production.
\item[Hybrid search] BM25 (keyword) + dense vector retrieval, fused (often RRF). watsonx Discovery default.
\item[InstructLab] IBM's open-source toolkit for community model customisation: taxonomy + synthetic data + multi-phase tuning.
\item[Instruct model] Fine-tuned to follow imperative instructions (``Summarise this'').
\item[JSONL] JSON-Lines format: one JSON object per line. The Tuning Studio input format.
\item[Kolmogorov--Smirnov test] Distribution-similarity test; compares two empirical CDFs.
\item[LangChain] Python / JS framework with chains, agents, tools, memory, retrievers, output parsers.
\item[LangGraph] LangChain sister project providing explicit state-machine workflows with conditional edges.
\item[LAB] Large-scale Alignment for chatBots. The InstructLab methodology (Sudalairaj et al., 2024).
\item[Llama] Meta's open-weight LLM family. Current on watsonx: \texttt{meta-llama/llama-3-3-70b-instruct}, \texttt{meta-llama/llama-3-2-*}.
\item[LlamaIndex] Alternative to LangChain, RAG-first.
\item[LoRA] Low-Rank Adaptation. Train two small matrices $A$, $B$ alongside frozen weights.
\item[MCP] Model Context Protocol. Open standard for exposing tools and data to LLM apps.
\item[Mistral / Mixtral] Mistral's model family. Current: \texttt{mistralai/mistral-large}, \texttt{mistralai/mixtral-*}.
\item[MoE] Mixture of Experts. Router activates a subset of expert sub-networks per token.
\item[Model Gateway] Fronting service for routing requests across multiple backing models / providers.
\item[Model Card] See Factsheet.
\item[PEFT] Parameter-Efficient Fine-Tuning umbrella term. Includes LoRA, prompt tuning, etc.
\item[PII] Personally Identifiable Information --- emails, phones, IDs, addresses.
\item[Prompt injection] Attacker text overrides developer instructions (``Ignore previous instructions\dots'').
\item[Prompt Lab] watsonx.ai's no-code prompt builder. Modes: Chat, Structured, Freeform.
\item[Prompt leaking] The model is tricked into revealing its system prompt.
\item[Prompt template] Versioned, named asset with variables, model binding, parameters, and (optional) few-shot examples.
\item[Prompt tuning] Train a learned soft prompt (continuous embeddings) prepended to inputs.
\item[QLoRA] LoRA on a 4-bit (NF4) quantised base model.
\item[Quantisation] Reducing the bit-width of weights (FP32 $\to$ FP16/BF16 $\to$ INT8 $\to$ INT4).
\item[RAG] Retrieval-Augmented Generation. Retrieve relevant chunks then generate.
\item[ReAct] Reason + Act loop. Core agent pattern.
\item[Re-ranker] Cross-encoder that re-scores retrieved candidates against the query.
\item[Reasoning model] LLM that emits an explicit chain-of-thought trace before its final answer.
\item[Repetition penalty] Sampling parameter that lowers the probability of already-emitted tokens.
\item[Random seed] Makes a sampling decoder reproducible.
\item[Slate] IBM's retrieval-specialised English embedder family: \texttt{ibm/slate-30m-english-rtrvr-v2}, \texttt{ibm/slate-125m-english-rtrvr-v2}.
\item[Soft prompt] Learned continuous embedding vectors prepended to inputs. Not human-readable.
\item[Stop sequence] A string that, once emitted, ends generation.
\item[Synthetic Data Generator] watsonx tool that creates statistically-similar synthetic tabular data from real samples or a custom schema.
\item[Taxonomy] InstructLab's YAML tree of skills and knowledge.
\item[Temperature] Decoding parameter that scales logits; higher = more diverse.
\item[Top-K / Top-P] Sampling controls. Top-K keeps the K most likely tokens; Top-P (nucleus) keeps the smallest set whose probability mass $\geq p$.
\item[Tuning Studio] watsonx.ai workspace for prompt tuning, LoRA, and full fine-tuning.
\item[Vector database] Storage + nearest-neighbour search for embeddings.
\item[Watson Assistant] IBM's conversational platform (often fronts watsonx.ai).
\item[Watson Discovery] IBM's classic enterprise search and document-understanding service.
\item[watsonx Discovery] Newer hybrid (BM25 + dense) retrieval service for the watsonx era.
\item[watsonx.ai] Studio for building, tuning, deploying foundation models.
\item[watsonx.data] Open lakehouse for data feeding watsonx.
\item[watsonx.governance] Lifecycle, risk, drift, and fairness controls.
\item[Zero-shot prompting] Prompt with no examples.
\end{description}

\cleardoublepage
