\chapter{One-Page Exam Cheat Sheet}
\label{app:cheatsheet}

\textbf{Print this page. Read it the morning of the exam.}

\section*{The numbers}
62 questions $\cdot$ 44 to pass (71\%) $\cdot$ 90 minutes $\cdot$ $\sim$87 s per question.

\section*{Blueprint --- spend study time here}
1. Analyse \& Design 15\% $\;$ 2. Prompt Engineering 16\% $\;$ \textbf{3. Fine-Tuning 31\%} $\;$ 4. RAG 17\% $\;$ 5. Deployment 13\% $\;$ 6. Integration 8\%.

\section*{Five capabilities}
Summarization $\cdot$ Classification $\cdot$ Generation (Code, Translation) $\cdot$ Extraction $\cdot$ Q\&A.

\section*{Patterns}
Transformer $\cdot$ MoE $\cdot$ VAE $\cdot$ Reasoning model.

\section*{Architecture decision tree}
Facts in model? $\to$ \textbf{Prompting}. Facts in our docs? $\to$ \textbf{RAG}. New behaviour/style? $\to$ \textbf{Fine-tune (PEFT/LoRA/InstructLab)}. Multi-step + tools? $\to$ \textbf{Agent}.

\section*{Current model IDs (2026)}
\begin{itemize}[leftmargin=*]
    \item Default Granite chat/instruct: \texttt{ibm/granite-3-2-8b-instruct}, \texttt{ibm/granite-3-3-8b-instruct}.
    \item Code: \texttt{ibm/granite-code-3-8b-instruct}. Vision: \texttt{ibm/granite-vision-3-2-2b}.
    \item Llama: \texttt{meta-llama/llama-3-3-70b-instruct}. Mistral: \texttt{mistralai/mistral-large}.
    \item Embedders: \texttt{ibm/slate-125m-english-rtrvr-v2}, \texttt{ibm/granite-embedding-278m-multilingual}.
    \item Safety: \texttt{ibm/granite-guardian-3-8b}, \texttt{ibm/granite-guardian-3-2-5b}.
    \item \emph{Deprecated --- recognise but don't pick:} \texttt{granite-13b-*}, \texttt{llama-2-*}, \texttt{flan-*}, \texttt{mpt-*}.
\end{itemize}

\section*{Billing classes (relative)}
Class 1 = embedders, small Granite $\cdot$ Class 2 = Granite 8B instruct $\cdot$ Class 3 = small third-party $\cdot$ Class 12 = Llama-3.3-70B, Mistral-Large $\cdot$ Class 13 = flagship/vision.

\section*{Parameter map (cause $\to$ knob)}
Too random $\to$ lower \texttt{temperature}, \texttt{top\_p}, switch to greedy. Output too short $\to$ \texttt{min\_new\_tokens}. Repetition loop $\to$ \texttt{repetition\_penalty} 1.1--1.2. Output runs forever $\to$ \texttt{max\_new\_tokens} + \texttt{stop\_sequences}. Reproducibility $\to$ \texttt{sample} + \texttt{random\_seed}.

\section*{Decoding}
\texttt{greedy} (deterministic, factual) $\cdot$ \texttt{sample} (creative, with temperature, top-k, top-p, random\_seed).

\section*{Fine-tuning ladder}
Few-shot $<$ Prompt tuning (soft prompt) $<$ LoRA $<$ QLoRA $<$ Full fine-tune $\;$ ; InstructLab adds taxonomy + SDG (LAB) + knowledge-then-skills phases.

\section*{Quantisation ladder}
FP32 $\to$ FP16/BF16 $\to$ INT8 (GPTQ, AWQ) $\to$ INT4 (NF4 / QLoRA).

\section*{LoRA core knobs}
$r \in \{4,8,16,32\}$, $\alpha = 2r$, target \texttt{q\_proj} + \texttt{v\_proj}, dropout 0.05.

\section*{Synthetic Data Generator}
Two modes: existing data $\cdot$ custom schema. Validate with \textbf{Kolmogorov--Smirnov} (overall) and \textbf{Anderson--Darling} (tails). DP: privacy budget $\varepsilon$ $\cdot$ leakage probability $\delta$ $\cdot$ random seed.

\section*{RAG checklist}
Chunk size 256--1024 with 10--20\% overlap $\cdot$ embed (Slate v2 / Granite Embedding) $\cdot$ index (HNSW) $\cdot$ retrieve $k$=3--5 $\cdot$ re-rank top-20 $\cdot$ ground prompt (``answer ONLY from context'') $\cdot$ Granite Guardian groundedness check.

\section*{Retrievers on the exam}
FAISS / Chroma (embedded) $\cdot$ Watson Discovery (legacy) $\cdot$ GitHub Code Retrieval API $\cdot$ \textbf{watsonx Discovery} (current IBM default) $\cdot$ pgvector / Elasticsearch / SingleStore (DB extensions).

\section*{Deployment}
Project (build) $\to$ Space (Dev) $\to$ Space (Staging) $\to$ Space (Prod) $\to$ REST. Use a \textbf{Model Gateway} to front multiple models. SaaS vs Software (Cloud Pak) by data residency. Refresh corpora with \textbf{watsonx AI Pipelines}.

\section*{Security filters}
\textbf{PII filter} $\cdot$ \textbf{HAP filter} $\cdot$ \textbf{Bias evaluator} $\cdot$ \textbf{Groundedness check}. All available via \textbf{Granite Guardian} and \textbf{watsonx.governance}.

\section*{LangChain primitives}
LLM / ChatWatsonx $\cdot$ Prompt Template $\cdot$ Chain $\cdot$ Tool $\cdot$ Agent $\cdot$ Memory $\cdot$ Retriever $\cdot$ Output Parser. For agents: \texttt{create\_tool\_calling\_agent} + \texttt{AgentExecutor}.

\section*{Open standard}
\textbf{MCP --- Model Context Protocol}: vendor-neutral way to expose tools and data to LLM agents.

\section*{Test-taking discipline}
3 passes: easy wins (45 min) $\to$ flagged hard (30 min) $\to$ review (15 min). Never leave blank. When in doubt, pick the \emph{Granite + RAG + governance} answer.

\cleardoublepage
